Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-12-31 astronum_2018/astronum-xrb.tex
fix typo
corrected typo in figure caption

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{xrb_profiles}
\caption{\label{fig:xrb_profiles} Vertical profiles at several laterial distances
  from the vertical axis through the plots shown in Figure~\ref{fig:xrb}.  These
  profiles sample the region behind and ahead of the flame.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.8\linewidth]{xrb_profiles}
\caption{\label{fig:xrb_profiles} Vertical profiles at several radial distances
  from the vertical axis through the plots shown in Figure~\ref{fig:xrb}.  These
  profiles sample the region behind and ahead of the flame.}
\end{figure}
